\LARGE \bf Detection of design pattern : A systematic mapping study

### 2016-01-02 article/main.tex
so far

After having queried the database and removed the duplicates, we exported the
results found as a .csv file and proceeded to screening.

@@

\begin{figure}
 \centering
  \begin{tabular}{ ccc }
   \bf Group & \bf \# of articles & \bf Cohen's kappa \\
   \hline {}
   1 & 132 & 0.88 \\
   2 & 133 & 0.66 \\
   3 & 134 & 0.91 \\
 \end{tabular}
 \caption{Cohen's Kappa coefficients}
\end{figure}

@@

Disagreement in the rating of article inside a pair were firstly dealt with a
reconsideration of the rating of each individual according to the arguments of his opposing rater.
In the case of unresolved disagreement, we brought our case before a senior
researcher that published in the studied field who would instruct us over the final
decision.
If even he could settle de disagreement, the article was included to possibly be
excluded at a later point.

\subsubsection{Cohen's kappa coefficient}
We calculated inter-rater agreement Cohen's kappa coefficient over the
rejection and acceptation of each articles, which gaves us an average coefficient
of 0.82.
Individual results for each pair of evaluators is given in \textit{Fig. 2}
alongside the number of articles assigned to each one.

@@

@@

Design pattern detection can be done either statically or dynamically.
So

@@

Of interest is the relation between the type of analysis and the type of
patterns detected. \textit{Fig. 5} and \textit{Fig. 6}
respectively presents the distribution of the number of articles and the
propotion.

@@

The majority of techniques are language dependent and the most used 
languages are Java and C++, but those detection methods can be easily converted to other languages
just by modifying the font-end.

Haotian and Shu[52] took a different approach by instrumenting Java bytecode

\subsection{Detection Level}
We found out that almost all of design patterns detection methods 
identify the patterns on a source code level, though, the detection could
be done on multiple levels.

@@

Systems based on rules are examples of gendeals with an inference engine for which

@@

%\begin{center}
%\includegraphics[scale=0.75]{validation_method.png}
%\end{center}

@@

A possible limitation of our studies is the selection of a unique source for 
the articles in Scopus.
This was done to facilitate our work in the extraction of relevant articles
since Scopus offers to export the results of a search query on its database.
It has been assumed that it does an exhaustive indexing of the journals
and conferences it references and that those sources includes most of the
relevant publications that covers software design pattern detection.
To mitigate the possibility of missing relevant articles we made sure that
Scopus indexes the big venues of software engineering (ACM, Springer, IEEE, and
???).

@@

There is a possibility for relevant articles to have been excluded at the
screening level due to a non representative title and abstract.
We believe the possibility to be unlikely since each article were screened by
two reviewers and that if the article had a possibly misleading title, it would
be rejected after a complete reading done before the classification phase.

>>>>

After having queried the database and removed the duplicates, we exported the
results found as a .csv file and proceeded to the screening.

@@

\begin{figure}
 \centering
  \begin{tabular}{ ccc }
   \bf Group & \bf \# of articles & \bf Cohen's kappa \\
   \hline {}
   1 & 132 & 0.88 \\
   2 & 133 & 0.66 \\
   3 & 133 & 0.91 \\
 \end{tabular}
 \caption{Cohen's Kappa coefficients}
\end{figure}

@@

Disagreement in the rating of article inside a pair were firstly dealt with a
reconsidaration of the rating by each individual according to the arguments of
his opposing rater.
In the case of unresolved disagreement, we brought our case before a senior
researcher that published in the studied field who would instruct us over the final
decision.
If even he couldn't settle de disagreement, the article was included to possibly be
excluded at a later point.

94 articles passed our exclusion scheme and thus the screening phase.

\subsubsection{Cohen's kappa coefficient}
Cohen's kappa coefficient is a measure of the inter-agreement between two rater
over the classification of a set of values.
A high coefficient value is indicative of a relative agreement between a pair
of raters.

We calculated inter-rater agreement Cohen's kappa coefficient over the
rejection and acceptation of each articles, which gaves us an average
coefficient of 0.81.
Individual results for each pair of evaluators is given in \textit{Fig. 2}
alongside the number of articles assigned to each one.

@@

Considering the number of articles that passed the screening phase

@@

Design pattern detection can be done either statically, dynamically or in
a combination of both.

A little bit less than half of the articles favoured a static approach to the
recognition of design motifs.

@@

Of interest is the relation between the type of analysis and the type of
patterns detected. \textit{Fig. 5} and \textit{Fig. 6}
respectively presents the distribution of the number of articles and their
proportion in this relation.

@@

The majority of techniques are language dependent and the most used 
languages are Java and C++, but those detection methods can be easily converted
to other languages by a simple modification of a font-end.

\subsection{Detection Level}

We found out that almost all of design patterns detection methods 
identify the patterns at the source code level, though, the detection could
be done on multiple levels.

When detection was done at multiple level, more often than not it was at both
the source and execution level.

@@

Systems based on rules are examples of general technique for which 
an inference engine is able to handle any patterns it has a rule for.
Di Martino and Esposito[40] presented a technique where ODOL is used
to describe the structural aspects of patterns.

@@

@@

A possible limitation of our studies is the selection of a unique source for 
the articles in Scopus.
This was done to facilitate our work in the extraction of relevant articles
since Scopus offers to export the results of a search query on its database.
It has been assumed that it does an exhaustive indexing of the journals
and conferences it references and that those sources includes most of the
relevant publications that covers software design pattern detection.
To mitigate the possibility of missing relevant articles we made sure that
Scopus indexes the big venues of software engineering (ACM, Springer and IEEE).

@@

There is a possibility for relevant articles to have been excluded at the
screening level due to a non representative title and abstract.
We believe the possibility to be unlikely since each article was screened by
two reviewers and that if the article had a possibly misleading title, it would
be rejected after a complete reading done before the classification phase.
